\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-02-09 jasa/paper-jasa.tex
Section 4.1: regenerate figures

Using the method outlined in Section~\ref{sec:approx},
figures~\ref{fig:2}, \ref{fig:3} and \ref{fig:4} show the approximated
ratio when using respectively a linear model, a neural network or a random
forest. The blue curve corresponds to the true target log-ratio, the green curve is
the direct approximation $\log \left( \frac{\hat s(\mathbf{x})}{1 - \hat s(\mathbf{x})} \right)$
without calibration, while the red curve is the approximation $\log \frac{\hat p(\hat
s(\mathbf{x}) | \theta_0)}{\hat p(\hat s(\mathbf{x}) | \theta_1)}$ as calibrated
using kernel density estimation for a fixed bandwidth set to $0.2$. Finally, the
cyan curve shows the approximated ratio when decomposing the mixtures, as
described in Section~\ref{sec:mixture}.

@@

    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2-b.pdf}
        \caption{Neural network}
        \label{fig:3}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2-c.pdf}
        \caption{Random forest}
        \label{fig:4}
    \end{subfigure}
    \caption{Approximation of the log-likelihood ratio $\log r(\mathbf{x};\theta_0,\theta_1) = \log \frac{p(\mathbf{x}|\theta_0)}{p(\mathbf{x}|\theta_1)}$ with calibrated classifiers. \glnote{I need to regenerate these figures using cross-validation for training and calibrating!}}\label{fig:animals}

>>>>

Using the method outlined in Section~\ref{sec:approx},
figures~\ref{fig:2}, \ref{fig:3} and \ref{fig:4} show the approximated
ratio when using respectively a linear model, a 2-layer neural network or a random
forest. The blue curve corresponds to the true target log-ratio, the green curve is
the direct approximation $\log \left( \frac{\hat s(\mathbf{x})}{1 - \hat s(\mathbf{x})} \right)$
without calibration, while the red curve is the approximation $\log \frac{\hat p(\hat
s(\mathbf{x}) | \theta_0)}{\hat p(\hat s(\mathbf{x}) | \theta_1)}$ as calibrated
using histograms. Finally, the
cyan curve shows the approximated ratio when decomposing the mixtures, as
described in Section~\ref{sec:mixture}.

@@

    \vspace{1em}

    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2-b.pdf}
        \caption{Neural network}
        \label{fig:3}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2-c.pdf}
        \caption{Random forest}
        \label{fig:4}
    \end{subfigure}
    \caption{Approximation of the log-likelihood ratio $\log r(\mathbf{x};\theta_0,\theta_1) = \log \frac{p(\mathbf{x}|\theta_0)}{p(\mathbf{x}|\theta_1)}$ with calibrated classifiers.}
